Neural and Symbolic Spatiotemporal Optimization of Cosmological Particle-Mesh Simulation

### 2023-05-18 docs/papers/sto/sto.tex
FIXUP draft: add coauthors

\author[Zhang, Li, Jamieson, et al.]{
%
Yucheng Zhang,$^{1, 2}$
%
Yin Li,$^{1, 3}$\thanks{Email: XYZ, eelregit@gmail.com, and XYZ}
%
and Drew Jamieson$^{4}$
%
\\$^1$Department of Mathematics and Theory, Peng Cheng Laboratory,
Shenzhen, Guangdong 518066, China
%
\\$^2$Center for Cosmology and Particle Physics, Department of Physics,
New York University, New York, NY 10003, USA
%
\\$^3$Center for Computational Astrophysics \& Center for Computational
Mathematics, Flatiron Institute, New York, NY 10010, USA
%
\\$^4$Max Planck Institute for Astrophysics, 85748 Garching bei
M\"unchen, Germany
}

>>>>

\author[Zhang, Li, Jamieson, et al.]{
%
Yucheng Zhang,$^{1, 2}$
%
Yin Li,$^{1, 3, 4}$\thanks{Email: XYZ, eelregit@gmail.com, and XYZ}
%
Drew Jamieson,$^{5}$
%
Libin Lu,$^{3}$
%
and XYZ
%
\\$^1$Department of Mathematics and Theory, Peng Cheng Laboratory,
Shenzhen, Guangdong 518066, China
%
\\$^2$Center for Cosmology and Particle Physics, Department of Physics,
New York University, New York, NY 10003, USA
%
\\$^3$Center for Computational Mathematics, Flatiron Institute, New
York, NY 10010, USA
%
\\$^4$Center for Computational Astrophysics, Flatiron Institute, New
York, NY 10010, USA
%
\\$^5$Max Planck Institute for Astrophysics, 85748 Garching bei
M\"unchen, Germany
}
